API design for machine learning software: experiences from the scikit-learn project

### 2013-10-19 paper.tex
Nitpicks in sections 1 and 2

As much as possible, \sklearn has been designed in such a way
as to avoid the proliferation of framework code.
We adopt simple conventions and limit the number of methods
an object must implement to a minimum.
The API is designed to adhere to the following principles:

@@

The choice to let a single object serve dual purpose as
estimator and model has been driven by usability and technical considerations.
Having two coupled instances
(an estimator object used as a factory, and a model object produced by the estimator)
makes a library harder to learn and use.
From the developer point of view, decoupling
estimators from models would create parallel class hierarchies and increases the
overall maintenance burden.
A good reason for decoupling would be to make it possible to ship a model
to a new environment where the full library cannot be installed.
However, our inspectable setup where model parameters are documented,
public attributes, and prediction formulas follow standard textbooks,
goes a long way in solving this problem.

>>>>

As much as possible, \sklearn has been designed in such a way
as to avoid the proliferation of framework code.
We adopt simple conventions and limit to a minimum the number of methods
an object must implement.
The API is designed to adhere to the following principles:

@@

The choice to let a single object serve dual purpose as
estimator and model has been driven by usability and technical considerations.
Having two coupled instances
(an estimator object used as a factory, and a model object produced by the estimator)
makes a library harder to learn and use.
From the developer point of view, decoupling
estimators from models would create parallel class hierarchies and increases the
overall maintenance burden.
A good reason for decoupling would be to make it possible to ship a model
to a new environment where the full library cannot be installed.
However, our inspectable setup where model parameters are documented
public attributes and prediction formulas follow standard textbooks,
goes a long way in solving this problem.
